---
title: "Getting RCPs into the atlas"
output: rmarkdown::github_document
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description of the data

Begin by loading some pre-processed data:
```{r}
load('./data/some_DAPI.RData')
```

In this case this is a segmentation data frame so lets check what variables are needed:

```{r}
head(segmentation)
```

We can test just to plot it first:
  
```{r}
plot(segmentation$x, segmentation$y, pch=16, cex=0.25, ylim=rev(range(segmentation$y)), asp=1)
```

Lets source the helper functions in R we need (they are located under the r folder in this Rproject)
```{r}
source('./r/helper_functions.R')
```

I downsampled the original image to 8255 x 9410 from the original 16510 x 18819 which is roughly 0.5.
So if your RCP centroids are in original pixel coordinates just downsample them `segmentation[,1:2] <- 0.5*segmentation[,1:2]`.

Other than that you are ready to just transform them to the atlas by this command:

```{r message=FALSE, results='hide',fig.keep='all', warning=FALSE}
#load in the sp and png package
if(!require("sp")){
  install.packages("sp")
  library("sp")
}
if(!require("png")){
  install.packages("png")
  library("png")
}
#load in the registration transformation
load('./data/ISS_regi6_5weeks.RData')
#get your dataset object
dataset<-rcp.to.atlas(regi, segmentation)
```

Lets check it out:
```{r}
head(dataset)
```
To get how many RCPs you have in agiven region check for example:
```{r}
table(dataset$acronym)
```

We can also plot this:

```{r}
par(mfrow=c(1,3), mar=c(0,0,0,0))
plot.regi(regi)
plot.regi(regi, draw.trans.grid = TRUE)
plot.regi(regi)
points(dataset$x, dataset$y, col = as.character(dataset$color), pch=16, cex=0.125)
```
